Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-13 article.qmd
Add arrows to figures

::: {#fig-ide layout-ncol=2 layout-valign="bottom"}
![](src/ide/ide1.png)

![](src/ide/ide2.png)

Screenshots of Visual Studio Code showing tooltips and highlighted type errors.
`Constant` are assigned with `assign(..., constant=True)` and can be used to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
The IDE automatically recognizes `e` as an `Equation`,
and provides autocompletion of the variables.
A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights
wrong names (`z` is not a name in `Model`)
and
mismatched types (`x` is `Variable` and `a` must be a number or a `Constant`)
:::
(add arrows to the figure)

>>>>

::: {#fig-ide layout-ncol=2 layout-valign="bottom"}
![](src/ide/ide1.svg)

![](src/ide/ide2.svg)

Screenshots of Visual Studio Code showing tooltips and highlighted type errors.
`Constant` are assigned with `assign(..., constant=True)` and can be used to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
The IDE automatically recognizes `e` as an `Equation`,
and provides autocompletion of the variables.
A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights
wrong names (`z` is not a name in `Model`)
and
mismatched types (`x` is `Variable` and `a` must be a number or a `Constant`)
:::
